---
title: "Final Report"
author: 
- "Todd Albertson"
- "Jenny Fingles"
- "Max McDonald"
- "Austin Sell"
date: "`r format(Sys.time(), '%B %d, %Y')`"
# abstract: "Abstract..."
output:
    pdf_document:
      fig_caption: yes
fontsize: 12pt
geometry: margin=1in
header-includes:
    - \usepackage{setspace}
    - \doublespacing
---

---
references:
- id: FakeyShenanigans2019
  title: "An example citation: Examples from an article of examples"
  author:
  - family: McFakerson
    given: Fakey F.
  - family: Shenanigans
    given: Bull
  container-title: QJBS
  volume: 1
  issue: 1
  page: 50-90
  type: article-journal
  issued:
    year: 2019
---

\pagebreak

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message=FALSE, warning=FALSE}
#loading necessary packages

library(lme4)
library(ggplot2)
```


```{r warning=FALSE}
data <- read.csv("https://github.com/arsell/599-Project/blob/master/cleandata.csv?raw=true")
```

# Introduction and Motivation

Here we can introduce our central research question. I don't believe citations are crucial to this project, but we can include them if necessary [@FakeyShenanigans2019].

# Data

Here is where we explain where the data comes from. Any descriptive statistics would be included here.

# Analysis

In this section we explain how our model is set up and any necessary assumptions. Model selection criteria should be included here as well.

# Results

We present the results of the model, including tables and/or figures. This should have the direct numerical interpretation of the key coefficients.

# Conclusion

Discussion of the substantive interpretation of the model, including any meaningful impact of findings as well as limitations of model.

\pagebreak

# References


