---
title: "Final Report"
author: 
- "Todd Albertson"
- "Jenny Fingles"
- "Max McDonald"
- "Austin Sell"
date: "`r format(Sys.time(), '%B %d, %Y')`"
# abstract: "Abstract..."
output:
    pdf_document:
      fig_caption: yes
fontsize: 12pt
geometry: margin=1in
header-includes:
    - \usepackage{setspace}
    - \doublespacing
---

---
references:
- id: FakeyShenanigans2019
  title: "An example citation: Examples from an article of examples"
  author:
  - family: McFakerson
    given: Fakey F.
  - family: Shenanigans
    given: Bull
  container-title: QJBS
  volume: 1
  issue: 1
  page: 50-90
  type: article-journal
  issued:
    year: 2019
---

\pagebreak

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
```

```{r}
#loading necessary packages

library(lme4)
library(ggplot2)
library(dplyr)
library(effects)
library(knitr)

options(scipen = 999)
options(digits = 6)
```


```{r}
data <- read.csv("https://github.com/arsell/599-Project/blob/master/data/cleandata.csv?raw=true")
data <- na.omit(data)
```


```{r echo=FALSE, results='hide'}
data$religion <- relevel(data$religion, ref="Other")

fit1 <- lm(educ ~ religion + age + region + wealthCat + urban, data=data)
summary(fit1)



fit2 <- lmer(educ ~ religion + age + wealthCat + urban + (1|region),
             data = data,
             REML = FALSE)
summary(fit2)

data$age2 <- data$age^2

fit3 <- lm(educ ~ religion + age + age2 + region + wealthCat + urban, data=data)
summary(fit3)

fit4 <- lmer(educ ~ religion + age + age2 + wealthCat + urban + (1|region),
             data = data,
             REML = FALSE)
summary(fit4)

fit5 <- lm(educ ~ religion + age + wealthCat*region + urban, data = data)
summary(fit5)

fit6 <- lmer(educ ~ (1|region),
             data = data,
             REML = FALSE)
summary(fit6)

fit7 <- lmer(educ ~ religion + age + urban + (1 + wealthCat|region),
             data = data,
             REML = FALSE)
summary(fit7)

fit8 <- lmer(educ ~ religion + age + urban + wealthCat + (1 + wealthCat|region),
             data = data,
             REML = FALSE)
summary(fit8)
```

```{r}
fit <- list(fit1, fit2, fit3, fit4, fit5, fit6, fit7, fit8)


bic.list <- NULL
for (i in 1:length(fit)){
  bic.list <- BIC(fit[[i]])
}

source("functions.R")
```

```{r eval=FALSE}
# WARNING: Cross-Validation take a substantial amount of time to run and is not evaluated by default.


#Running in serial

mae1 <- get_mae(fit1, data, method="lm")
mae2 <- get_mae(fit2, data, method="lmer")
mae3 <- get_mae(fit3, data, method="lm")
mae4 <- get_mae(fit4, data, method="lmer")
mae5 <- get_mae(fit5, data, method="lm")
mae6 <- get_mae(fit6, data, method="lmer")
mae7 <- get_mae(fit7, data, method="lmer")
mae8 <- get_mae(fit8, data, method="lmer")
```

```{r eval=FALSE}
# WARNING: Cross-Validation take a substantial amount of time to run and is not evaluated by default.
# Additionally, this chunk is written to take advantage of parallel processing on multiple cores. It should not be run in conjunction with the above chunk.


# Running in parallel
library(parallel)
library(foreach)
library(doParallel)

numCores <- detectCores()
registerDoParallel(numCores)

mae <- foreach (i=1:length(fit), .combine = c) %dopar% {
  if (i == 1 | i == 3 | i == 5){
    get_mae_lm(fit[[i]], data)
  } else {
    get_mae_lmer(fit[[i]], data)
  }
}

mae1 <- mae[1] # 2.496750
mae2 <- mae[2] # 2.496738
mae3 <- mae[3] # 2.496008
mae4 <- mae[4] # 2.495984
mae5 <- mae[5] # 2.490587
mae6 <- mae[6] # 3.051729
mae7 <- mae[7] # 2.489470
mae8 <- mae[8] # 2.487023

```

# Introduction and Motivation

Our research examines the educational attainment of women in Honduras. While there are many things that can play a role in education, we strive to examine the impact of religion and wealth.

# Data

Our data comes from Demographic and Health Surveys (DHS). Specifically, we pull from the responses of over 15,000 Honduran women in 20XX. The data that we use in our analysis includes years of education, age, religion, wealth, urbanicity, and region.


# Analysis

Two primary concerns motivated the model construction. First, we examined the possibility of a curvilinear impact of age on education. The figure below reveals that there is a slight increase in education before a gradual decline in the older generation. Notably, the variance of education also increases with age. We think that there are likely two effects present here. The first is that young adults now are far more likely to pursue education now than they were a few decades ago. Thus, the older generations have lower levels of education. The second effect is that as you age, the probability of attaining additional years of education increases, which is evidence from the initial bump that we observe. Given the cross-sectional nature of our data, we cannot disentangle these effects. As such, we model age as a quadratic function which we believe (and our model diagnostics show) is the best fit for the mix of these effects.

```{r}
# Investigate age vs educ relationship
p1 <- ggplot(data = data,
             aes(x = age,
                 y = educ)) +
  geom_point(position = "jitter") +
  stat_smooth(geom = "smooth") +
  xlab("Age") +
  ylab("Years of Education") +
  ggtitle("Exploration of Non-linear trend in Education by Age")

p1
```


The second concern we have is the heterogenous distribution of key variables across the administrative regions of Honduras. As can be seen in the two figures below, we observe very noticeable differences in both education and wealth across the different regions of Honduras. Additionally, these patterns seem to overlap. To account for the variation across the administrative regions, we fit random intercepts for these regions. We also considered the possibility of included region-fixed effects, but leave-one-out cross-validation revealed that random intercepts performed the best.

```{r out.width= "50%"}
include_graphics("../maps/avgs_by_region1.pdf")
include_graphics("../maps/avgs_by_region3.pdf")
```

```{r eval = FALSE, out.width= "85%"}
include_graphics("../maps/avgs_by_region2.pdf")
```

```{r eval = FALSE, out.width= "85%"}
include_graphics("../maps/avgs_by_region3.pdf")
```


The final model that we fit is defined as the following:

$EDUC_{ij} = \beta_0 + \beta_1 AGE_{ij} + \beta_2 AGE^2_{ij} + \beta_3 WEALTH_{ij} + \beta_4 RELIGION_{ij} + \beta_5 URBAN_{ij} + \mu_j + \epsilon_{ij}$

$\epsilon_{ij} \sim N(0,\sigma^2)$

$\mu_j \sim N(0,\tau^2)$

The years of education for individual $i$ in region $j$ are predicted by the above model where $WEALTH$ and $RELIGION$ are factor variables, and $\mu_j$ is the random intercept for each region.

# Results

The two primary takeaways are below.

```{r}

effs <- as.data.frame(effect(c("wealthCat"), fit4))

data.p1 <- data %>%
  group_by(wealthCat) %>%
  summarise(prop_urban = mean(urban))
effs <- cbind(effs, data.p1[,2])

effs$wealthCat <- reorder(effs$wealthCat, effs$fit)

wealth_bar <- ggplot(effs,
                     aes(x = wealthCat,
                         y = fit, 
                         fill = prop_urban)) +
  geom_col() +
  geom_errorbar(aes(ymin = lower,
                    ymax = upper),
                width=0.2) +
  xlab("Wealth Category") +
  ylab("Predicted Years of Education") +
  labs(fill = "% Urban") +
  ggtitle("Predicted Education by Wealth")

wealth_bar
```

```{r}

effs.religion <- as.data.frame(effect(c("religion"), fit4))

data.p2 <- data %>%
  group_by(religion) %>%
  summarise(prop_urban = mean(urban))
effs.religion <- cbind(effs.religion, data.p2[,2])

religion_bar <- ggplot(effs.religion,
                     aes(x = religion,
                         y = fit, 
                         fill = prop_urban)) +
  geom_col() +
  geom_errorbar(aes(ymin = lower,
                    ymax = upper),
                width=0.2) +
  xlab("Religion") +
  ylab("Predicted Years of Education") +
  labs(fill = "% Urban") +
  ggtitle("Predicted Education by Religion")

religion_bar

```

# Conclusion

Discussion of the substantive interpretation of the model, including any meaningful impact of findings as well as limitations of model.

\pagebreak

# References


